Using Metric Space Indexing for Complete and Efficient Record Linkage

### 2018-02-19 paper.tex
Update on Overleaf.

We now describe the datasets and method used in our
evaluation~\footnote{The raw experimental data, additional figures and
the source code required to run these experiments can be downloaded
from the following repository. \\
\url{http://github.com/digitisingscotland/pakdd2018-metric-linkage}.}.
We used three datasets from two
domains in our experiments, as summarised in Table~\ref{table-datasets}.
The first is \emph{Cora}~\cite{Cora2017}, which contains 1,295 records
that refer to 112 machine learning publications. Cora is commonly used
as a benchmark dataset in the literature for assessing linkage
algorithms. Ground truth is provided via a unique \emph{paper\_id}
identifier of the form ``blum1993". In this experiment linkage is
performed over the same set of records (i.e.\ a
de-duplication~\cite{Chr12}).

>>>>

We now describe the datasets and method used in our
evaluation~\footnote{Experimental data, additional figures and
source code can be downloaded from:
\url{http://github.com/digitisingscotland/pakdd2018-metric-linkage}.}.
We used three datasets from two
domains in our experiments, as summarised in Table~\ref{table-datasets}.
The first is \emph{Cora}~\cite{Cora2017}, which contains 1,295 records
that refer to 112 machine learning publications. Cora is commonly used
as a benchmark dataset in the literature for assessing linkage
algorithms. Ground truth is provided via a unique \emph{paper\_id}
identifier of the form ``blum1993". In this experiment linkage is
performed over the same set of records (i.e.\ a
de-duplication~\cite{Chr12}).
